% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{enumitem,xcolor}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}



% Set your name here
\def\name{Hector Bahamonde}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}
% \href{http://www.hectorbahamonde.com}{www.HectorBahamonde.com}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {political science, economic development, methods},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{{\tiny \name}}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
 Department of Philosophy, Contemporary History and Political Science\\
 University of Turku, Finland\\
 Assistentinkatu 7, Turku 20014\\
  \\
  \\
\begin{footnotesize}
CV last updated: \today. \\
\href{http://github.com/hbahamonde/Job_Market/raw/master/Bahamonde_CV.pdf}{\texttt{{\color{red} Download latest CV here}}}.%\\
%\href{http://www.hectorbahamonde.com/jobmarket/}{\texttt{{\color{red} Download latest application materials here}}}.
\end{footnotesize}

\end{minipage}
 \hspace{\fill}\begin{minipage}{0.35\linewidth}
  \begin{tabular}{rr}
    \texttt{e}: & \href{mailto:hibano@utu.fi}{hibano@utu.fi} \\
    \texttt{w}: & \href{http://www.hectorbahamonde.com}{www.HectorBahamonde.com}\\
    \texttt{Zoom ID}: & \href{https://us02web.zoom.us/j/9513261038?pwd=S3BSWXQxZW11NC9CRjRoMmd0TkpEZz09}{\texttt{951-326-1038}}\\
    \\
    \\
    \\
    \\
    \\
  \end{tabular}
\end{minipage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\input{/Users/hectorbahamonde/Job_Market/CV_education.tex}\unskip}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic Employment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Academic Employment}

{\input{/Users/hectorbahamonde/Job_Market/CV_academic_employment.tex}\unskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appointments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Appointments}

\begin{itemize}
  \item[\textcolor{gray}{\textbullet}] {\bf Program Coordinator}: Public Administration UOH, 2018.
  \item[\textcolor{gray}{\textbullet}] {\bf Researcher}: Labor Studies UOH, 2020---today.
  \item[\textcolor{gray}{\textbullet}] {\bf Researcher}: Millennium Institute, Foundational Research on Data, 2020---today.
  \item[\textcolor{gray}{\textbullet}] {\bf Editorial Board Member}: ``\emph{Social Sciences}'' journal, Springer Nature, 2020---today.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Interest -- Dissertation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Research}
{\input{/Users/hectorbahamonde/Job_Market/CV_overview_research.tex}\unskip}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Working Papers -- Published Papers
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\input{/Users/hectorbahamonde/Job_Market/CV_research.tex}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conferences
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Conference Talks}

{\input{/Users/hectorbahamonde/Job_Market/CV_conferences.tex}\unskip}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Invited Talks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Invited Talks}

{\input{/Users/hectorbahamonde/Job_Market/CV_invited_talks.tex}\unskip}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Media Appearances
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Media Appearances and Op-Eds}

  \begin{itemize}

    \item[\textcolor{gray}{\textbullet}] ``\href{https://www.nytimes.com/2021/08/04/opinion/biden-eviction-covid-democrats.html}{Biden's Honeymoon Is Over, and He Knows It}.''\\\textcolor{gray}{New York Times: August 4th. 2021.}

    \item[\textcolor{gray}{\textbullet}] ``{\color{blue}Plan Paso a Paso y Pobreza: Factores Atenuantes en la Región de O'Higgins}.''\\With Carolina Rodriguez (UOH). \href{https://www.elrancaguino.cl/2021/04/14/opinion-plan-paso-a-paso-y-pobreza-factores-atenuantes-en-la-region-de-ohiggins/}{ElRancaguino.cl}, \href{https://ohigginsaldia.cl/2021/04/14/plan-paso-a-paso-y-pobreza-factores-atenuantes-en-la-region-de-ohiggins/amp/?__twitter_impression=true}{O'HigginsAlD\'ia.cl}, \href{https://www.poderyliderazgo.cl/opinion-plan-paso-a-paso-y-pobreza-factores-atenuantes-en-la-region-de-ohiggins/}{PoderyLiderazgo.cl}: {\color{gray} April 14th-15th. 2021.}

    \item[\textcolor{gray}{\textbullet}] ``\href{https://cooperativa.cl/noticias/pais/region-de-ohiggins/investigadores-pronostican-que-se-podrian-perder-mas-de-35-mil-empleos/2020-09-27/110705.html}{Investigadores pronostican que se podr\'ian perder m\'as de 35 mil empleos por la pandemia en O'Higgins}.''\\\textcolor{gray}{Cooperativa.cl: September 27th. 2020.}
   
    \item[\textcolor{gray}{\textbullet}] ``\href{https://cooperativa.cl/noticias/pais/region-de-ohiggins/investigadores-pronostican-que-se-podrian-perder-mas-de-35-mil-empleos/2020-09-27/110705.html}{Investigadores pronostican que se podr\'ian perder m\'as de 35 mil empleos por la pandemia en O'Higgins}.''\\\textcolor{gray}{Cooperativa.cl: September 27th. 2020.}
   
    \item[\textcolor{gray}{\textbullet}] ``\href{https://www.elrancaguino.cl/2020/09/24/gerentas-en-la-region-de-ohiggins-y-precariedad-laboral-donde-estamos-como-region/}{Gerentas en la Regi\'on de O'Higgins y Precariedad Laboral: ¿D\'onde estamos como Regi\'on?}''\\With Cristina Hern\'andez (UOH). \textcolor{gray}{ElRancaguino.cl: September 24th. 2020.}
   
    \item[\textcolor{gray}{\textbullet}] ``\href{https://www.diarioelpulso.cl/2020/08/25/uso-de-conceptos-politicos-en-epocas-de-campanas-electorales-nos-merecemos-mas/}{Uso de Conceptos Pol\'iticos en \'Epocas de Campa\~nas Electorales: Nos merecemos m\'as}.''\\With Mariela Soto (UOH). \textcolor{gray}{DiarioElPulso.cl: August 25th. 2020.}
   
    \item[\textcolor{gray}{\textbullet}] ``\href{https://eltipografo.cl/2019/07/desigualdad-y-democracia-en-chile}{Desigualdad y Democracia en Chile}.''\\\textcolor{gray}{ElTip\'ografo.cl: July 9th. 2019.}


  \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Grants
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Grants, Fellowships, \& Awards}
{\input{/Users/hectorbahamonde/Job_Market/CV_grants.tex}\unskip}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Teaching}

{\input{/Users/hectorbahamonde/Job_Market/CV_teaching.tex}\unskip}

\begin{enumerate}
\item[\Pointinghand]  {\bf Also I would be very happy to teach the entire methods sequence (undergraduate and/or graduate)}, including but not limited to: {\color{gray}time series and panel-data methods, experiments and causal inference for the social sciences, epistemology and qualitative methods, statistics for the social sciences (frequentist/Bayesian) and statistical programming}. I can be very flexible and take care of the needs of the institution.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Referee
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Referee for}
  \begin{itemize}
    \item[\textcolor{gray}{\textbullet}] Political Behavior, Third World Quarterly, The Oxford Encyclopedia of Political Decision Making, Journal of Iberian and Latin American Research, Revista Chilena de Derecho y Ciencia Pol\'itica, Sociological Inquiry, Social Sciences, Revista de Ciencia Pol\'itica.
  \end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section*{Service}

\begin{itemize}
\item[\textcolor{gray}{\textbullet}] Coordinator: \emph{ICSO-UOH Speaker Series}, 2020---2021.
\item[\textcolor{gray}{\textbullet}] Panel Discussant: MPSA 2018.
\item[\textcolor{gray}{\textbullet}] Panel Chair: WPSA 2018, APSA 2019 (full paper panel organizer).
\item[\textcolor{gray}{\textbullet}] Graduate student representative. CPE/IPE job search (2015). \emph{Rutgers University}.
\item[\textcolor{gray}{\textbullet}] Discussant ``Emerging Trends Topics'' talks (2014, 2015). \emph{Rutgers University}.
\item[\textcolor{gray}{\textbullet}] Graduate Student Mentor (2014-2017). \emph{Rutgers University}.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section*{References}
\begin{itemize}
\item[\textcolor{gray}{\textbullet}] Robert Kaufman: {\textcolor{gray}{\scriptsize Professor, Rutgers University.}}
\item[\textcolor{gray}{\textbullet}] Daniel Kelemen: {\textcolor{gray}{\scriptsize Professor and Jean Monnet Chair in European Union Politics, Rutgers University.}}
\item[\textcolor{gray}{\textbullet}] Paul Poast: {\textcolor{gray}{\scriptsize Associate Professor, Department of Political Science, University of Chicago.}}
\item[\textcolor{gray}{\textbullet}] Juan Pablo Luna: {\textcolor{gray}{\scriptsize Associate Professor, Political Science Institute and School of Government (joint appointment), Catholic University---Chile.}}
\item[\textcolor{gray}{\textbullet}] Ludovico Feoli: {\textcolor{gray}{\scriptsize Executive Director Center for Inter American Policy and Research, Research Associate Professor, Tulane University.}}
\item[\textcolor{gray}{\textbullet}] Ross Baker: {\textcolor{gray}{\scriptsize Distinguished Professor, Rutgers University.}}
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Misc
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Misc}
{\input{/Users/hectorbahamonde/Job_Market/CV_misc.tex}\unskip}




\bigskip



\end{document}
