
\newpage
{\bf Sample Student Evaluations and Teaching References}. 

Professor Dr. Ross Baker, Distinguished Professor - Rutgers University, has more details about my teaching skills. His letter can be accessed via the Interfolio system. Please \href{mailto:bahamondeh@gmail.com}{let me know} if you wish to read the letter. Also, you can always \href{mailto:bahamondeh@gmail.com}{send me an email} to receive the latest teaching evaluations. However, here I summarize some of my student's comments I have received during my three years of teaching assistant experience:


{\scriptsize
\begin{itemize}

\item \emph{``The TA is very responsive when spoken to and is quick to answer questions via email. The TA's willingness to learn with us is also helpful in learning the material and allows us to have nice discussions in class.''}

\item \emph{``My TA showed he knew his subject material because he was able to answer hard and complicated questions efficiently despite it being obvious that English was not his first language.''}

\item \emph{``Hector showed me how to make connections with government terms. He made the big picture seem simpler for me.''}

\item \emph{``Over the break, I came to the conclusion that I want to major in political science. American Government was the first course I ever took related to political science, and I loved it.''}

\item \emph{``I am very grateful for your help and will definitely reach out to you to ask questions about Comparative Politics if that's what I eventually plan on doing. I feel like I'm very new to this whole field of study - mainly because I haven't been in the US for a very long time, and because of the way the government works so differently here than in Pakistan, where I'm from.''}

\item \emph{``The teaching assistant really helped me to think about all the ``why'' aspects of the material. Like for example, ``Why is this important?'' or ``Why does this relate to the material?''.''}

\item \emph{``The best TA in teaching the course material. Each recitation session is well compact with main concepts crucial for understanding the course material.''}

\item \emph{``As an international student who takes the course for requirement, the TA have greatly increase my interest in politics, increase my awareness of politics.''}

\item \emph{``Hector Bahamonde was very engaging and I learned alot in recitation. I liked that he was always prepared with examples to relate what we learn in class to today's world. He has a very cool perspective on politics.''}

\item \emph{``I think everything was perfect with the recitations.''}

\item \emph{``Easily the best TA I have had at Rutgers. He engaged the class, and presented the material in an interesting and extremely organized manner. I was nervous about taking this class because it is not one of my specialties, but after the first recitation I realized that I would learn a lot and Hector really changed my attitude towards taking the class.''}

\item \emph{``Hector encourages us to get involved during recitation. Normally I wouldn't raise my hand as often, but he makes it easy to participate in class.''}

\end{itemize}

}

