% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}


% email input begin
\newread\fid
\newcommand{\readfile}[1]% #1 = filename
{\bgroup
  \endlinechar=-1
  \openin\fid=#1
  \read\fid to\filetext
  \loop\ifx\empty\filetext\relax% skip over comments
    \read\fid to\filetext
  \repeat
  \closein\fid
  \global\let\filetext=\filetext
\egroup}
\readfile{/Users/hectorbahamonde/RU/Bibliografia_PoliSci/email.txt}
% email input end

% Set your name here
\def\name{Hector Bahamonde, PhD}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}
% \href{http://www.hectorbahamonde.com}{www.HectorBahamonde.com}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {political science, economic development, methods},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{{\tiny \name}}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
 Center for Inter-American Policy \& Research \\
  Tulane University \\
  Richardson Hall \\
  205 Richardson, New Orleans, LA 70118\\
  \\
\begin{footnotesize}
 CV last updated: \today. \\
 \href{http://github.com/hbahamonde/Job_Market/raw/master/Bahamonde_NA_CV.pdf}{\texttt{{\color{red}Download latest CV here}}}.
 \end{footnotesize}

\end{minipage}
 \hspace{\fill}\begin{minipage}{0.35\linewidth}
  \begin{tabular}{rr}
   \texttt{cp}: & +1(732)318-9650 \\
    \texttt{e}: & \href{mailto:\filetext}{\filetext} \\
    \\
    \\
    \\
    \\
    \\
  \end{tabular}
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Career Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Career Objective}

I want to help institutions (big or small) to reach their goals by incorporating my experience as an academic. By bringing my analytical skills, and excellent interpersonal relationships, I am interested in both leading teams and collaborating with others. My ideal institution lets its employees be innovative, goal-oriented and creative.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\input{/Users/hectorbahamonde/RU/Job_Market/CV_education.tex}\unskip}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic Employment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Academic Employment}

{\input{/Users/hectorbahamonde/RU/Job_Market/CV_academic_employment.tex}\unskip}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Non-Academic Employment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Non-Academic Employment}

\begin{itemize}
  \item[] {\bf \emph{Departamento Provincial Santiago Sur}, Ministry of Education (Chile)}\\
    Chief of Staff, 2012.

  \item[] {\bf Office of Rep. Cristian Monckeberg (23rd District, Chile)}\\
    Constituent Services, 2011.

  \item[] {\bf United Nations Development Programme (Santiago, Chile)}\\
    Internship, 2010.

  \item[] {\bf Part Time Consultant (different projects)}\\
    Data analyst and coordinator, 2006-2011.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conferences and Invited Talks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Public Outreach}
  % Conferences
  {\input{/Users/hectorbahamonde/RU/Job_Market/CV_conferences.tex}\unskip}
  % Invited Talks
  {\input{/Users/hectorbahamonde/RU/Job_Market/CV_invited_talks.tex}\unskip}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Training}

{\input{/Users/hectorbahamonde/RU/Job_Market/CV_teaching.tex}\unskip}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Grants
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Funds Granted as a Principal Investigator}
{\input{/Users/hectorbahamonde/RU/Job_Market/CV_grants.tex}\unskip}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Interest
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Academic Overview}
{\input{/Users/hectorbahamonde/RU/Job_Market/CV_overview_research.tex}\unskip}

\subsection*{Creative Writing}
{\input{/Users/hectorbahamonde/RU/Job_Market/CV_research.tex}\unskip}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Misc
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Misc}

\subsection*{Skills}
Trained as an academic, I have considerable experience as an independent critical person, used to work under pressure, and goal-oriented. Not only I have good writing/analytical skills, but also excellent interpersonal relationships. Having both excellent leadership skills, and willingness to collaborate with others, make me an ideal candidate to take different roles, for instance in different projects, in the same institution. 


{\input{/Users/hectorbahamonde/RU/Job_Market/CV_misc.tex}\unskip}




\bigskip



\end{document}
