\begin{itemize}
\item[\textcolor{gray}{\textbullet}] {\bf American Political Science Association (APSA)}: \textcolor{gray}{2016 (Philadephia, PA, U.S.), 2019 (Washington D.C.---full panel organizer), 2020 (San Francisco, CA, U.S.).}
\item[\textcolor{gray}{\textbullet}] {\bf European Political Science Association (EPSA)}: \textcolor{gray}{2022 (Prague, Czech Republic), 2023 (Glasgow, Scotland), 2024 (Cologne, Germany).}
\item[\textcolor{gray}{\textbullet}] {\bf European Consortium for Political Research (ECPR)}: \textcolor{gray}{2022 (Innsbruck, Austria---full panel organizer).}
\item[\textcolor{gray}{\textbullet}] {\bf Nordic Sociological Association Conference (NSA)}: \textcolor{gray}{2022 (Reykjavik, Iceland).}
\item[\textcolor{gray}{\textbullet}] {\bf Midwest Political Science Association (MPSA, Chicago)}: \textcolor{gray}{2017, 2018 (declined), 2020 (canceled---COVID19), 2023, 2024.}
%\item[\textcolor{gray}{\textbullet}] {\bf Society for Institutional \& Organizational Economics (SIOE)}: \textcolor{gray}{2022 (Toronto, Canada; declined).}
\item[\textcolor{gray}{\textbullet}] {\bf Italian Association for the History of Economic Thought (ISPE)}: \textcolor{gray}{2019 (Bologna, Italy).}
\item[\textcolor{gray}{\textbullet}] {\bf Italian Political Science Association (SISP)}: \textcolor{gray}{2023 (Genova, Italy).}
\item[\textcolor{gray}{\textbullet}] {\bf \emph{Red de Econom\'ia Pol\'itica para Am\'erica Latina} (REPAL)}: \textcolor{gray}{2019 (New Orleans, LA, U.S.).}
\item[\textcolor{gray}{\textbullet}] {\bf Latin American Studies Association (LASA)}: \textcolor{gray}{2014 (Chicago, IL, U.S.), 2015 (San Juan, Puerto Rico; declined), 2016 (NYC, NY, U.S.), 2018 (Barcelona, Spain), 2022 (San Francisco, CA, U.S.), 2023 (Vancouver, Canada).}
\item[\textcolor{gray}{\textbullet}] {\bf Nordic Latin American Research Network (NOLAN)}: \textcolor{gray}{2024 (Copenhagen, Denmark).}
\item[\textcolor{gray}{\textbullet}] {\bf Western Political Science Association (WPSA)}: \textcolor{gray}{2015 (Las Vegas, NV, U.S.), 2016 (San Diego, CA, US; declined), 2018 (San Francisco, CA, US declined).}
\item[\textcolor{gray}{\textbullet}] {\bf Southern Political Science Association (SPSA)}: \textcolor{gray}{2015 (New Orleans, LA, U.S.), 2018 (New Orleans, LA, U.S.), 2020 (San Juan, Puerto Rico; declined), 2023 (St. Petersburg, FL, U.S.), 2024 (New Orleans, LA, U.S.).}
\item[\textcolor{gray}{\textbullet}] {\bf Chilean Political Science Association (ACCP, Santiago)}: \textcolor{gray}{2010, 2023.}

%\item[\textcolor{gray}{\textbullet}] {\bf Development Economics and Policy Conference (German Economic Association)}: \textcolor{gray}{2018 (Zurich, Switzerland; declined).}
%\item[\textcolor{gray}{\textbullet}] {\bf \emph{Red Interamericana para la Educaci\'on en Administraci\'on P\'ublica y Ciencia Pol\'itica}}: \textcolor{gray}{2019 (Concepci\'on, Chile).}
\end{itemize}
