\begin{itemize}

	%\item[\textcolor{gray}{\textbullet}] Fondecyt Iniciaci\'on 2022 \#11220303, ANID, Chile. Sponsorship: \emph{Millennium Institute, Foundational Research on Data}, Chile. Length: March 15th 2022---March 14th 2025. Amount: $\sim$ \$96,000 USD (in 2022 prices).

	
	\item[\textcolor{gray}{\textbullet}] Domestic and International Conference Travel Support: 
		\begin{itemize}
			
			\item[$-$] \emph{Department of Political Science} and \emph{School of Arts and Sciences}, Rutgers University (both fall and spring awards in 2013, 2014, 2015 and 2016).
			
			\item[$-$] \emph{Stone Center for Latin American Studies}, Tulane University (2017).

			\item[$-$] \emph{Center for Inter-American Policy and Research}, Tulane University (2018).
		\end{itemize}
	
	\item[\textcolor{gray}{\textbullet}] Teaching Assistantship Appointment. \emph{Department of Political Science} and \emph{School of Arts and Sciences}, Rutgers University (2015, 2016, 2017).
	
	\item[\textcolor{gray}{\textbullet}] Small Grant Fund for Research on Latin America. \emph{Center for Latin American Studies}, Rutgers University (2013).
	
	\item[\textcolor{gray}{\textbullet}] Teaching Assistant Professional Development Fund. \emph{School for Arts and Sciences}, Rutgers University (2015, 2016, 2017).
	
	\item[\textcolor{gray}{\textbullet}] Pre-Dissertation Award. \emph{Department of Political Science}, Rutgers University (2016).
	
	\item[\textcolor{gray}{\textbullet}] Experimental Workshop Award. \emph{Center for the Experimental Study of Politics and Psychology}, Rutgers University (2015).
	
	\item[\textcolor{gray}{\textbullet}] Jerome M. Clubb Scholarship. \emph{Inter-university Consortium for Political and Social Research} (2013).
	
	\item[\textcolor{gray}{\textbullet}] Excellence Fellowship. \emph{School for Arts and Sciences}, Rutgers University (2012). Tuition remission, health benefits and stipends, for five years of doctoral studies.
\end{itemize}