%%%%%%%%%%%%%%%%%%%%
% Working Papers
%%%%%%%%%%%%%%%%%%%%
\subsection*{Peer-Reviewed Articles}


\begin{itemize}

	\item[\textcolor{gray}{\textbullet}] \href{https://link.springer.com/article/10.1057/s41269-020-00174-4}{\fullcite{Bahamonde2020a}}.

	\item[\textcolor{gray}{\textbullet}] \href{https://doi.org/10.1016/j.ejpoleco.2021.102048}{\fullcite{Bahamonde2021a}}

	\item[\textcolor{gray}{\textbullet}] \href{https://doi.org/10.1111/rsp3.12337}{\fullcite{Modrego2020}}

	\item[\textcolor{gray}{\textbullet}] \href{https://journals.sub.uni-hamburg.de/giga/jpla/article/view/1121/1128}{\fullcite{Bahamonde2018}}

	\item[\textcolor{gray}{\textbullet}] \href{https://scielo.conicyt.cl/pdf/revcipol/v31n2/art07.pdf}{\fullcite{Luna2011}}
  
\end{itemize}

%\subsection*{Under Review, Revise and Resubmit, Submitted}

%	\begin{itemize}



%  	\end{itemize}


\subsection*{Work in Progress}


\begin{itemize}

	%\item[\textcolor{gray}{\textbullet}] \href{https://github.com/hbahamonde/Conjoint_US/raw/master/Bahamonde_Quininao_Conjoint_Letter_PA.pdf}{\input{/Users/hectorbahamonde/research/Conjoint_US/title_letter.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/research/Conjoint_US/status_letter.txt}\unskip}}. With Crist\'obal Qui\~ninao (UOH).

  	\item[\textcolor{gray}{\textbullet}] \href{https://raw.githubusercontent.com/hbahamonde/Economic_Experiment_Vote_Selling/master/abstract.txt}{\input{/Users/hectorbahamonde/research/Economic_Experiment_Vote_Selling/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/research/Economic_Experiment_Vote_Selling/status.txt}\unskip}}. With Andrea Canales (UOH).

  	\item[\textcolor{gray}{\textbullet}] \href{https://raw.githubusercontent.com/hbahamonde/Physical/main/abstract.txt}{\input{/Users/hectorbahamonde/research/Physical/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/research/Physical/status.txt}\unskip}}. With Outi Sarpila (UTU).

  	\item[\textcolor{gray}{\textbullet}] \href{https://github.com/hbahamonde/Bahamonde_Kovac/raw/master/Bahamonde_Kovac.pdf}{\input{/Users/hectorbahamonde/research/Bahamonde_Kovac/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/research/Bahamonde_Kovac/status.txt}\unskip}}. With Heikki Kaupi (UTU), Wilma Nissila (UTU) and Igor Kovac (U Cincinnati).


	%\item[\textcolor{gray}{\textbullet}] \href{https://raw.githubusercontent.com/hbahamonde/Bus/master/abstract.txt}{\input{/Users/hectorbahamonde/research/Bus/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/research/Bus/status.txt}\unskip}}. With Felix Modrego (UOH) and Andrea Canales (UOH).

	\item[\textcolor{gray}{\textbullet}] \href{https://raw.githubusercontent.com/hbahamonde/Tobalaba/master/abstract.txt}{\input{/Users/hectorbahamonde/research/Tobalaba/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/research/Tobalaba/status.txt}\unskip}}. With Paz Irarrazabal (Universidad de Chile).

	%\item[\textcolor{gray}{\textbullet}] Machine Learning and Political Ideology in the U.S.: An Experimental Case Study using SMOTE, {\bf \emph{in preparation}}. With Crist\'obal Qui\~ninao (UOH).

	%\item[\textcolor{gray}{\textbullet}] \href{https://github.com/hbahamonde/Conjoint_US/raw/master/Bahamonde_Quininao_Conjoint.pdf}{\input{/Users/hectorbahamonde/research/Conjoint_US/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/research/Conjoint_US/status.txt}\unskip}}. With Crist\'obal Qui\~ninao (UOH).

	%\item[\textcolor{gray}{\textbullet}] \href{https://raw.githubusercontent.com/hbahamonde/IncomeTaxAdoption/master/abstract.txt}{\input{/Users/hectorbahamonde/Dissertation/Papers/IncomeTaxAdoption/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/Dissertation/Papers/IncomeTaxAdoption/status.txt}\unskip}}.

	%\item[\textcolor{gray}{\textbullet}]  \href{https://github.com/hbahamonde/Earthquake_Paper/raw/master/Bahamonde_Earthquake_Paper.pdf}{\input{/Users/hectorbahamonde/Dissertation/Papers/Earthquake_Paper/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/Dissertation/Papers/Earthquake_Paper/status.txt}\unskip}}.

  %	\item[\textcolor{gray}{\textbullet}] \href{https://raw.githubusercontent.com/hbahamonde/Negative_Link_Paper/master/abstract.txt}{\input{/Users/hectorbahamonde/Dissertation/Papers/NegativeLink/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/Dissertation/Papers/NegativeLink/status.txt}\unskip}}. 

  	\item[\textcolor{gray}{\textbullet}] \href{https://raw.githubusercontent.com/hbahamonde/Running_Tally/master/abstract.txt}{\input{/Users/hectorbahamonde/research/Running_Tally/title.txt}\unskip}, {\bf \emph{\input{/Users/hectorbahamonde/research/Running_Tally/status.txt}\unskip}}. With Richard Lau (Rutgers University) and Mona Kleinberg (UMass - Lowell). 

\end{itemize}


%%%%%%%%%%%%%%%%%%%%
% Other Publications
%%%%%%%%%%%%%%%%%%%%


\subsection*{Book Reviews in Peer-Reviewed Journals (Invited)}

\begin{itemize}
	\item[\textcolor{gray}{\textbullet}] In\'es Dur\'an Matute (2019). \href{https://doi.org/10.1080/13260219.2019.1671679}{``Indigenous Peoples and the Geographies of Power: Mezcala's Narratives of Neoliberal Governance''} (Routledge). \emph{Journal of Iberian and Latin American Research}. % Scopus
\end{itemize}

\subsection*{Book Chapters}

\begin{itemize}
\item[\textcolor{gray}{\textbullet}] \href{http://www.vanderbilt.edu/lapop/chile/Chile-2010-cultura-politica.pdf}{?`Estable Pero Sin Ra\'ices? Los Partidos Pol\'iticos Chilenos en la Opini\'on P\'ublica}, in \emph{Cultura Pol\'itica de la Democracia en Chile, Ch. IX, LAPOP Country Report, 2010}. With Juan Pablo Luna, Germ\'an Bidegain, Roody Reserve and Giancarlo Visconti.
\end{itemize}



