\begin{enumerate}

\item {\bf O\'\unskip Higgins University}:
  
    \begin{itemize}
      \item[$\bullet$] \href{https://github.com/hbahamonde/Metodos_Cuanti_I/raw/master/Bahamonde_Metodos_Cuanti_I.pdf}{``Quantitative Methods''} (Instructor, \emph{undergraduate}, \texttt{T1}: 2020).
      \item[$\bullet$] \href{https://github.com/hbahamonde/Ciencia_Politica_I/raw/master/Bahamonde_Ciencia_Politica_I.pdf}{``Political Science I''} (Instructor, \emph{undergraduate}, \texttt{T1}: 2020).
      \item[$\bullet$] \href{https://github.com/hbahamonde/Metodos_de_Investigacion/raw/master/Bahamonde_Metodos_de_Investigacion.pdf}{``Research Methods''} (Instructor, \emph{undergraduate}, \texttt{T2}: 2019).
      \item[$\bullet$] \href{https://github.com/hbahamonde/Intro_Ciencias_Sociales/raw/master/Bahamonde_Intro_Ciencias_Sociales.pdf}{``Introduction to Social Sciences''} (Instructor, \emph{undergraduate}, \texttt{T1}: 2019).
      \item[$\bullet$] \href{https://github.com/hbahamonde/Social_Sciences_Epistemology_UGRAD/raw/master/Bahamonde_Social_Sciences_Epistemology_UGRAD_Syllabus.pdf}{``Social Sciences and Epistemology''} (Instructor, \emph{undergraduate}, \texttt{T2}: 2018).
    \end{itemize}

\item {\bf Tulane University}:
  
    \begin{itemize}
      \item[$\bullet$] \href{https://github.com/hbahamonde/Comparative_Politics_UGRAD/raw/master/Bahamonde_Comparative_Politics_Syllabus_UGRAD.pdf}{``Introduction to Comparative Politics''} (Instructor, \emph{undergraduate}, \texttt{spring}: 2018).
    \end{itemize}

\item {\bf Rutgers University}:

    \begin{itemize}
      \item[$\bullet$] \href{http://github.com/hbahamonde/Math-Camp/raw/master/Syllabus/Math_Camp_Syllabus.pdf/}{``Math and Computing Camp for Political Scientists''} (Instructor, \emph{graduate}, \texttt{winter}: 2015).
      
      \item[$\bullet$] ``Introduction to Quantitative Methods'' (TA, \emph{graduate}, \texttt{fall}: 2015).
      
      \item[$\bullet$] ``American Government'' (TA, \emph{undergraduate}, \texttt{fall}: 2014 to \texttt{spring}: 2017).
    \end{itemize}

\end{enumerate}